The Effects of weather on maize yields: New evidence from Kenya

### 2018-12-19 writing/draft3/draft17.tex
writing at home

\pdfminorversion=4
\submitto{\ERL}
\makesavenoteenv{tabular}

@@

We further applied a series of likelihood ratio tests of significance of random slopes, however no subset of random slopes improved the fit. Hence, besides the fixed effects, our final model only included random intercepts.\footnote{Although adding the random slope of the coefficient of variation slightly improved the AIC from $2122.226$ to $2122.110$, we decided to not to include the coefficient of variation of temperature in the random effects. The reason for not including the random slope is that the difference in AIC is negligible and the F-test of the comparison of the two models is insignificant favouring the simpler model (p-value$=0.128$).}

To verify our results, we adapted an alternative step-down model building
approach using the Satterthwaite’s method to determine the p-values of the individual
t-tests \cite{lmerTest}. We started with a model which included the complete set of our weather measures in both fixed effects and random effects. In the first part of the procedure, the insignificant random effects were removed one by one. In each iteration, the insignificant variable with the highest p-value was removed and this was repeated until only the significant predictors remained. After this, we applied an analogous procedure to the fixed effects until we were left only with the significant ones. As recommended in literature, we considered the level of significance $\alpha=0.1$ for random effects and $\alpha=0.05$~ for fixed effects \cite{lmerTest}. This method lead to the same model as the one obtained with our primary AIC-based method described above.

>>>>

%\pdfminorversion=4
\submitto{\ERL}
\makesavenoteenv{tabular}

@@

We further applied a series of likelihood ratio tests to test for significance of random slopes. No subset of the random slopes improved the fit, therefore besides the fixed effects, our final model only included the random intercepts.\footnote{Although adding the random slope of the coefficient of variation slightly improved the AIC from $2122.226$ to $2122.110$, we decided to not to include the coefficient of variation of temperature in the random effects. The reason for not including the random slope is that the difference in AIC is negligible and the F-test of the comparison of the two models is insignificant favouring the simpler model (p-value$=0.128$).}

To verify our results, we adapted an alternative step-down model building
approach using the Satterthwaite’s method to determine the p-values of the individual
t-tests \cite{lmerTest}. We started with a model which included the complete set of our weather measures in both fixed effects and random effects. In the first part of the procedure, the insignificant random effects were removed one by one. In each iteration, the insignificant variable with the highest p-value was removed . This was repeated until only the significant predictors remained. After this, we applied an analogous procedure to the fixed effects until we were left only with the significant ones. As recommended in literature, we considered the level of significance $\alpha=0.1$ for random effects and $\alpha=0.05$~ for fixed effects \cite{lmerTest}. This method led to the same model as the one obtained with our primary AIC-based method described above.
